A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2019-01-29 paper/submission/ZW10157-response-1.tex
adding some of linda's edits to response.

@@

{\bf Our response:} {\color{blue} 
	To address this concern, the following was added on lines XX-XX in the updated manuscript:
	The AWA facility operates at both low and high charge charge (up to 100 nC). Strong non-linearities
at high charge justify using a full 3D space charge approach. Finding optics solutions in this regime and 
with the tight aperture constraints specific to two beam acceleration at the AWA is not trivial.

At the same time, AWA is a facility where many different accelerator research experiments take
place. Therefore it is very desirable, and was an important research objective, to develop a precise, e.g. 3D
model embedded into a multi-objective optimization framework. In this way, optimization of various 
machine configurations can be done at different charge levels. While other codes such as GPT  and ELEGANT, also have integrated genetic optimization algorithms; the OPAL framework, differentiates itself by being open source (i.e. free to use), massively parallel, and fully 3D.
}

>>>>

Thank you for considering the manuscript.
We appreciate the constructive criticism. 
It helped improve the quality of the manuscript.

@@

{\bf Our response:} {\color{blue} 
	To address this concern, the following was added on lines XX-XX in the updated manuscript:

A hallmark of the AWA facility is the flexibility to swap physical
components in the beamlines, which enables different, often novel,
accelerator research experiments to take place.  Not only do the
physical machine components change, the beam characteristics also vary
considerably to meet different needs.  The facility operates at both low
and high charge (up to 100 nC), and at high charge strong nonlinearities
require a full 3D space charge approach in simulations for modeling.  
Finding optics solutions in this regime, especially when
there are additional constraints such as the small aperture two-beam
accelerating structures, is challenging even without the quick
turnaround of the beamline configurations.  Therefore, it has been an
important research objective to develop a precise, e.g. 3D model
embedded into a multi-objective optimization framework that may be used
as a flexible platform for optimization of changing machine
configurations operated at different charge levels. While other codes
such as GPT [updated ref here] and ELEGANT [updated ref here], also have
integrated genetic optimization algorithms; the OPAL framework,
differentiates itself by being open source (i.e. free to use), massively
parallel, and fully 3D.
}

### 2019-01-29 paper/submission/prab.tex
adding some of linda's edits to response.

%Unfortunately, the island parallelization approach is not well suited for
  %running search algorithms in the massively parallel environment.
%The decision how many processors are assigned to an island is non-trivial.
%\todo{PA: what are roles?}
%Parallel performance is sensitive to placement and assignment of roles to
  %processors of such frameworks and therefore should be considered carefully.
%Especially the master thread on an island (used to exchange individuals
  %between the islands and aggregate solutions) can be overwhelmed with
  %messages from slaves evaluating individuals.
%This creates hotspots on the network and as a result the network performance
  %suffers.

@@

%
Using the default expression primitives this can be stated in an input file
  as:
%
%\vspace{0.2cm}
\iffalse
\begin{samepage}
	\begin{flushleft}
		\begin{Verbatim}[fontsize=\scriptsize]
		d1: DVAR, VARIABLE="x1", LOWERBOUND="-1.0", UPPERBOUND="1.0";
		d2: DVAR, VARIABLE="x2", LOWERBOUND="-1.0", UPPERBOUND="1.0";
		d3: DVAR, VARIABLE="x3", LOWERBOUND="-1.0", UPPERBOUND="1.0";

		obj1: OBJECTIVE,
		EXPR="1- exp(-1 * (sq(x1 - 1/sqrt(3)) 
		+ sq(x2 - 1/sqrt(3)) + sq(x3 - 1/sqrt(3))))";
		obj2: OBJECTIVE,
		EXPR="1- exp(-1 * (sq(x1 + 1/sqrt(3)) 
		+ sq(x2 + 1/sqrt(3)) + sq(x3 + 1/sqrt(3))))";

		objs:    OBJECTIVES = (obj1, obj2);
		dvars:   DVARS = (d1, d2, d3);
		constrs: CONSTRAINTS = ();
		opt: OPTIMIZE, OBJECTIVES=objs, DVARS=dvars, CONSTRAINTS=constrs;
		\end{Verbatim}
	\end{flushleft}
\end{samepage}
\fi

@@

A general-purpose framework for solving multi-objective
  optimization problems was presented.
Its modular design simplifies the application to simulation-based optimization
  problems for a wide range of problems and allows to exchange the
  optimization algorithm.
%In a recent work, we successfully implemented and integrated another
  %optimization algorithm, originally presented in~\cite{pesc:11}, into our
 % framework.
The flexibility of being able to adapt both ends of the optimization
  process, the forward solver and the optimization algorithm simultaneously
  not only leads to broad applicability but it facilitates
  tailoring the optimization strategy to the optimization problem as well.

%This first study shows that the framework is ready to tackle problems arising
%  in the domain of beam dynamics.
%
%Interestingly, the computation of a good approximation of the Pareto front is
%  already feasible on a small cluster using only a modest number of MPI
%  processes.
%  
%For 1000 generations consisting of 2048 feasible and 8354 infeasible function
%  evaluations (simulations) the optimizer needed $845$ minutes on the
%  \textsc{Felsim} cluster on $16$ processes.
%
%When we double the number of processes to $32$ (\textsc{Felsim} allows a
%  maximum of $64$ processes per job) the runtime improves to $302$ minutes (2048
%  accepted and 5426 infeasible individuals).
%Notice that the runtime can vary due to the random nature of the process.
%Nevertheless we see a reasonable speeduo when using more cores to solve the
%  optimization problem. %and the parallel performance will be further evaluated
%  in a forthcoming publication.
%The number of individuals is the only limiting factor.
The framework was integrated into OPAL, and used 
to study a beam dynamics problem at the AWA.
A scan of time step and hyper parameters was done to determine computational settings.
Then a full scale physics optimization was performed.
Optimization of the 3D beam size and energy spread was accomplished.
The TBA beam line presented is currently being installed at the AWA.
Once installation is complete, 
the results shown here will guide future experiments at the AWA.
%This problem also took advantage of the frameworks massively parallel capabilities by
%running on 2624 processes on Bebop at LCRC.

>>>>

@@

@@

A general-purpose framework for solving multi-objective
  optimization problems was presented.
Its modular design simplifies the application to simulation-based optimization
  problems for a wide range of problems and allows to exchange the
  optimization algorithm.
The flexibility of being able to adapt both ends of the optimization
  process, the forward solver and the optimization algorithm simultaneously
  not only leads to broad applicability but it facilitates
  tailoring the optimization strategy to the optimization problem as well.

The framework was integrated into OPAL, and used 
to study a beam dynamics problem at the AWA.
A scan of time step and hyper parameters was done to determine computational settings.
Then a full scale physics optimization was performed.
Optimization of the 3D beam size and energy spread was accomplished.
The TBA beam line presented is currently being installed at the AWA.
Once installation is complete, 
the results shown here will guide future experiments at the AWA.
